The MIT License (MIT)

Copyright (c) 2015 Donovan Squires

Permission is hereby granted, free of charge, to any person obtaining a copy
of this software and associated documentation files (the "Software"), to deal
in the Software without restriction, including without limitation the rights
to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
copies of the Software, and to permit persons to whom the Software is
furnished to do so, subject to the following conditions:

The above copyright notice and this permission notice shall be included in all
copies or substantial portions of the Software.

THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
SOFTWARE.

%preamble copies main document for testing
%comment when including in main doc.
%=============================================
% \documentclass{article}
% \usepackage{setspace}
% \usepackage{graphicx,calc,pdfpages}
% \usepackage[letterpaper,margin=1.5in]{geometry}
% \usepackage{indentfirst}
% \usepackage{float}
% \usepackage{caption,subcaption}
% \usepackage{longtable,pdflscape}
% \usepackage{amsmath}
% \usepackage[hidelinks]{hyperref}
% \usepackage{appendix}

% \doublespacing

% \begin{document}
%=============================================




\begin{centering}
\begin{singlespace}
	INSTRUMENTATION ELECTRONICS FOR AN INTEGRATED \\ ELECTROPHYSIOLOGY DATA ACQUISITION \\ AND STIMULATION SYSTEM
		
	\vspace{2\baselineskip}
%	\vfill
	
	Donovan Squires, M.S.E.\\
	\vspace{\baselineskip}
	Western Michigan University, 2013
\end{singlespace}	
\end{centering}

\vspace{0.5\baselineskip}

The Neurobiology Engineering Laboratory at Western Michigan University has need of an electrophysiology instrumentation system combining generation of multiple arbitrary stimulation waveforms and recording of action potentials on multiple channels.  Electronics for an instrumentation system with the capability of generating four unique stimulation waveforms and recording action potentials on eight channels were developed and implemented on a printed circuit board.  Collaboration with fellow graduate student, Mr.~Kyle Batzer, who developed firmware and software for the instrumentation system as described in his thesis, was essential for successful realization of the instrumentation system.  Knowledge gained and reported by previous students working in the Neurobiology Engineering laboratory also contributed to the development.  This system was used to perform a standard electrophysiology
experiment on earthworm giant axon action potentials using only instrumentation electronics and software developed by students at Western Michigan University.




%=============================================
% \thispagestyle{empty}	
% \end{document}
